Contextual Combinatorial Cascading Bandits

### 2016-01-19 contextual combinatorial cascading bandits.tex
update proof for general case

\newcommand{\CLemmaPrefixExi}{
  Suppose $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the conjunctive objective, there exists a prefix $B$ of $A$ such that 
  $$
    p_{\wedge, t, B} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{B}}', \qquad R_{\wedge}(t, B) \geq \frac{1}{2} R_{\wedge}(t, A).
  $$ 
}
\newcommand{\CLemmaSumXiEstimateInDet}{
  If $\lambda \geq C_\gamma$, then
  $$
    \sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln \left(\frac{\det(\bV_t)}{\lambda^d} \right).
  $$
}
\newcommand{\CLemmaDetVt}{
  $\det(\bV_t)$ is increasing with respect to $t$ and 
  $$
    \det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.
  $$
}

@@

\paragraph{Lipschitz continuity}
The expected reward function $f(A, w)$ is a Lipschitz continuous with respect to $w$ together with position discount parameters $\gamma_k, k\leq K$. In particular, there is a constant $B>0$ such that, for any $w,w'$, we have
$$
	|f(A, w) - f(A, w')| \leq B\sqrt{\sum_{k=1}^{|A|} \gamma_k^2(w(a_k) - w'(a_k))^2},
$$
where $A = (a_1, \ldots, a_{|A|})$.

@@

@@

If we define a function $f$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS, w = (w(1), \ldots, w(L))$ by
\begin{align}
	&f: \cS \times [0,1]^E \to [0,1] \nonumber \\
	&f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_k' \prod_{i = 1}^{k - 1} w(a_i)(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
\label{eq:functionfstar}
\end{align}
then we have $\br_{t} = f(\bA_t, \bw_t)$ and $\EE[\br_{t}] = f(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$.

@@

The next lemma provides some properties about a prefix of action $A$ in the conjunctive case, which leads to the finding of a prefix $B$ of $A$ with similar regret and probability of full observation as those of $A$, as given in Lemma~\ref{lem:prefixexists}.
\begin{lemma} %lem:prefixRelation
  \label{lem:prefixRelation}
  Suppose $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. 
  Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. 
  Suppose we have expected weights $w$ for the base arms of action $A$. 
  Let $p_{\wedge, A}$ be the {\em probability of full observation of $A$}, that is the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ are observed under the conjunctive objective:
  $$
    p_{\wedge, A} = \prod_{k=1}^{\abs{A}-1} w_{a_k}.
  $$
  Then for the problem with conjunctive objective and $k < \abs{A}$, we have the following properties:
  \begin{itemize}
  	\item[(1)] $f_{\wedge}(A, w) \leq \gamma_{\abs{A}}' + (1 - \gamma_{\abs{A}}') p_{\wedge, A}$;
  	\item[(2)] $f_{\wedge}(B_{k+1}, w) \leq f_{\wedge}(B_k, w)$;
  	\item[(3)] $p_{\wedge, B_{k+1}} \leq p_{\wedge, B_k}$;
  	\item[(4)] $f_{\wedge}(B_k, w) \leq \gamma_{k+1}' + (1 - \gamma_{k+1}') p_{\wedge,B_{k+1}}$.
  \end{itemize}
\end{lemma}
\begin{proof}
  Let $m = |A|$.
  By the definition of $f_{\wedge}(A,w)$ in Eq.~\eqref{eq:functionfstar}, we have
  \begin{itemize}
  	\item[(1)]
  	\begin{align*}
  	  f_{\wedge}(A,w) & = \sum_{k = 1}^{\abs{A}} \gamma_k' \prod_{i = 1}^{k - 1} w(a_i) (1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i) \\
  	  &\leq \gamma_m'(1 - p_{\wedge, A} w_m) + p_{\wedge, A} w_m \\
  	  &\leq \gamma_m' + (1 - \gamma_m') p_{\wedge, A};
  	\end{align*}

  	\item[(2)]
  	\begin{align*}
  	  &f_{\wedge}(B_k, w) - f_{\wedge}(B_{k+1}, w)\\
  	  &=\prod_{i=1}^{k}w_i - \gamma_{k+1}' (\prod_{i=1}^{k}w_i) (1 - w_{k+1}) - (\prod_{i=1}^{k}w_i) w_{k+1}\\
  	  &=(1 - \gamma_{k+1}') (\prod_{i=1}^{k}w_i) (1 - w_{k+1}) \geq 0;
  	\end{align*}

  	\item[(3)]
  	$p_{\wedge, B_{k+1}} = \prod_{i=1}^{k} w_i \leq \prod_{i=1}^{k-1} w_i = p_{\wedge, B_k}$;

  	\item[(4)]
  	\begin{align*}
  	  f_{\wedge}(B_k, w) & \leq \gamma_{k}' (1 - p_{\wedge,B_{k+1}}) + p_{\wedge,B_{k+1}}\\
  	  &\leq \gamma_{k+1}' (1 - p_{\wedge,B_{k+1}}) + p_{\wedge,B_{k+1}} \\
  	  &= \gamma_{k+1}' + (1 - \gamma_{k+1}') p_{\wedge,B_{k+1}}
  	  \end{align*}
 \end{itemize}
\end{proof}

\begin{lemma} %lem:prefixexists
  \label{lem:prefixexists}
  \CLemmaPrefixExi
\end{lemma}
\begin{proof}
  Let $w= \theta_*^{\top} x_t$.
  If $f_{\wedge}(A, w) \geq \frac{1}{2} f_{\wedge, t}^{\ast}$, then by Lemma \ref{lem:prefixRelation} (1),
  $$
    p_{\wedge, t, A} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{A}}'.
  $$
  In this case, we set prefix $B = A$.

  Now suppose $f_{\wedge}(A, w) \leq \frac{1}{2} f_{\wedge, t}^{\ast}$. Let
  $$
    x_k = f_{\wedge}(B_k,w), ~~ y_k = \gamma_k' + (1 - \gamma_k')p_{\wedge, t,B_k}, ~~I_k = [x_k, y_k]
  $$
  Then by Lemma \ref{lem:prefixRelation}, we have $x_k \leq y_k$, $x_{k+1} \leq x_k \leq y_{k+1}$. Therefore, $I_k$ is indeed an interval and $I_k \cap I_{k+1} \neq \emptyset$. Also, $x_{\abs{A}} = f_{\wedge}(A, w)$ and $y_1 = 1$. Thus
  $$
    [f_{\wedge}(A,w), 1] = \bigcup_{k=1}^{\abs{A}} I_k.
  $$
  Then there exists a $k$ such that $\frac{1}{2}f_{\wedge, t}^{\ast} \in I_k$:
  $$
    f_{\wedge}(B_k,w) \leq \frac{1}{2}f_{\wedge, t}^{\ast} \leq \gamma_k' + (1 - \gamma_k')p_{\wedge, t, B_k}
  $$
  Therefore, the results are derived.
\end{proof}

The following lemma provides the important result on the regret at each time $t$ in terms of feature vectors of base arms at the time.
\begin{lemma} %lem:DeltaEstimate
  \label{lem:DeltaEstimate}
  For any time $t$ and $A = (a_1, \ldots, a_{\abs{A}})$, if $f(A_t^*, \bU_t) \leq f(A, \bU_t)$, then we have
  $$
    R(t,A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}};
  $$
  if $f_{\wedge}(A_t^*, \bU_t) \leq f_{\wedge}(A, \bU_t)$, then we have
  $$
    R_{\wedge}(t, A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
  $$
\end{lemma}
\begin{proof}
  By Lemma \ref{lem:estimateU}, $\theta_{\ast}^{\top}x_t \leq \bU_t$. Then by Lemma \ref{lem:increasing},
  $$
    f_t^{\ast} = f(A_t^{\ast}, \theta_{\ast}^{\top}x_t) \leq f(A_t^{\ast}, \bU_t).
  $$
  By Lemma \ref{lem:estimateTech} and the definition of $\bU_t$ in Eq.\eqref{eq:defU},
  $$
    f(A, \bU_t) \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
  $$
  By our condition that $f(A_t^{\ast}, \bU_t) \leq f(A, \bU_t)$, we have 
  $$
    f_t^{\ast} \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
  $$
  Therefore,
  $$
    R(t, A) = f_t^{\ast} - f(A, \theta_{\ast}^{\top}x_t) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
  $$
  The result for the conjunctive case can be deduced in a similar way.
\end{proof}

@@

\begin{lemma} %lem:DeltaEsimateWithP*
  \label{lem:DeltaEsimateWithP*}
  Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$.
  Suppose the equation (\ref{eq:estimateTheta}) holds for time $t-1$. Then
  $$
    \EE_t[R(t, \bA_t)] \leq \frac{1}{p^*} \EE_t \left[ \bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
  $$
  If we have
  $$
    \gamma_K' \le \frac{1}{4} f_{\wedge}^{\ast} = \frac{1}{4} \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast},
  $$
  then
  $$
    \EE_t [R_{\wedge}(t, \bA_t) ] \leq \frac{8}{f_{\wedge}^{\ast}} \EE_t \left[ \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
  $$
\end{lemma}
\begin{proof}
  For the disjunctive case,  
  \begin{align}
    &\EE[R(t, \bA_t)|\cH_t]  \nonumber \\
    =& \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \label{eq:addOt}\\
    =& \EE \left[ \left. R(t, \bA_t) \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right] \label{eq:removeE}\\
    \leq &\frac{1}{p^{\ast}} \EE \left[ \left. R(t, \bA_t) \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right] \label{eq:relaxpstar}\\
    \leq &\frac{1}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right] \label{eq:useradiusbound}\\
    \leq &\frac{1}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\bO_t} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \right| \cH_t \right]. \label{eq:relaxindicator}
  \end{align}
  Equality \eqref{eq:addOt} is because when $\bA_t$ is fixed, $p_{t, \bA_t}$ is the probability of $\bO_t\geq\abs{\bA_t}$, and thus the inner expectation is $1$. 
  Equality \eqref{eq:removeE} is because when the history $\cH_t$ is fixed, $\bA_t$ is fixed by the deterministic algorithm C$^3$-UCB, and thus there is no need to write the conditional expectation. 
  Inequality~\eqref{eq:relaxpstar} is because $p_{t,\bA_t} \geq p^*$ by definition. 
  Inequality~\eqref{eq:useradiusbound} is by Lemma \ref{lem:DeltaEstimate} and the fact $f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t)$, which is true because algorithm C$^3$-UCB selects action $\bA_t$ as the best action with respect to $\bU_t$. 
  Inequality~\eqref{eq:relaxindicator} is by simply arguing on the two cases for the indicator function $\bOne\{\bO_t\geq\abs{\bA_t}\}$.

  For the conjunctive case, by Lemma~\ref{lem:prefixexists} there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, t, \bB_t} \geq \frac{1}{2}f_{\wedge, t}^* - \gamma'_{|\bB_t|}$ and $R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t)$. 
  By the assumption that $\gamma'_{|\bB_t|}\le \gamma'_K \le \frac{1}{4} f^*_{\wedge} \le \frac{1}{4} f^*_{\wedge,t}  $, we have $p_{\wedge, t, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$. 
  Then, similar to the derivation from Eq.\eqref{eq:addOt} to Eq.\eqref{eq:relaxpstar}, we have
  \begin{align}
    &\EE_t[R_{\wedge}(t, \bA_t)] \leq 2 \EE[R_{\wedge}(t, \bB_t) \left. \right| \cH_t] \nonumber \\
    =& 2 \EE \left[ \left. R_{\wedge}(t, \bB_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\} \right| \bB_t \right]  \right| \cH_t \right] \nonumber \\
    =& 2\EE \left[ \left. R_{\wedge}(t, \bB_t) \frac{1}{p_{\wedge, t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right] \nonumber \\
    \leq &\frac{8}{f_{\wedge, t}^{\ast}} \EE \left[ \left. R_{\wedge}(t, \bB_t) \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right]. \label{eq:btOneotbt}
  \end{align}
  Next, we have
  \begin{equation} \label{eq:andstarbt}
    f_{\wedge}(A_t^*, \theta_*^{\top}x_t) \leq f_{\wedge}(A_t^*,\bU_t) \leq f_{\wedge}(\bA_t,\bU_t) \leq f_{\wedge}(\bB_t,\bU_t),
  \end{equation}
  where the first inequality is by Lemmas \ref{lem:estimateU} and \ref{lem:increasing}, the second inequality is by the C$^3$-UCB algorithm, in which the best action $\bA_t$ is selected with respect to $\bU_t$, and the last inequality is by Lemma~\ref{lem:prefixRelation}~(2).

  Then by Lemma \ref{lem:estimateTech},
  \begin{equation} \label{eq:btuttrue}
    f_{\wedge}(\bB_t,\bU_t) \leq f_{\wedge}(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k\bbeta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
  \end{equation}
  Therefore, combining Eq.\eqref{eq:andstarbt} and \eqref{eq:btuttrue}, we have
  \begin{align}
    R_{\wedge}(t, \bB_t) & = f_{\wedge, t}^{\ast} - f_{\wedge}(\bB_t, \theta_{\ast}^{\top}x_t) \nonumber \\
    & \leq \sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}. \label{eq:sumbetax}
  \end{align}
  Finally from Inequalities~\eqref{eq:btOneotbt} and \eqref{eq:sumbetax}， we can derive the result
  \begin{align*}
    &\EE_t[R_{\wedge}(t, \bA_t)] \\
    \leq& \frac{8}{f_{\wedge, t}^*} \EE \left[\bOne\{ \bO_t \geq \abs{\bB_t} \}\sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
    \leq& \frac{8}{f_{\wedge}^*} \EE \left[ \sum_{k=1}^{ \bO_t } \bbeta_{t-1}(\delta) \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
  \end{align*}
\end{proof}

>>>>

\newcommand{\CLemmaPrefixExi}{
	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the conjunctive objective, there exists a prefix $B$ of $A$ such that 
	$$
	p_{t, B} \geq \frac{1}{2}f_{t}^{\ast} - 1 + \gamma_{\abs{B}}, \qquad R(t, B) \geq \frac{1}{2} R(t, A).
	$$ 
}
\newcommand{\CLemmaSumXiEstimateInDet}{
  If $\lambda \geq C_\gamma$, then
  $$
    \sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln \left(\frac{\det(\bV_t)}{\lambda^d} \right).
  $$
}
\newcommand{\CLemmaDetVt}{
  $\det(\bV_t)$ is increasing with respect to $t$ and 
  $$
    \det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.
  $$
}

@@

\paragraph{Lipschitz continuity}
The expected reward function $f(A, w)$ is a Lipschitz continuous with respect to $w$ together with position discount parameters $\gamma_k, k\leq K$. In particular, there is a constant $B>0$ such that, for any $w,w'$, we have
$$
	|f(A, w) - f(A, w')| \leq B \sum_{k=1}^{|A|} \gamma_k |w(a_k) - w'(a_k)|,
$$
where $A = (a_1, \ldots, a_{|A|})$.

@@

\subsubsection{General Results}

@@

If we define a function $f$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS, w = (w(1), \ldots, w(L))$ by
\begin{align}
	&f: \cS \times [0,1]^E \to [0,1] \nonumber \\
	&f(A,w) = \sum_{k = 1}^{\abs{A}} (1 - \gamma_k) \prod_{i = 1}^{k - 1} w(a_i)(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
\label{eq:AndRewardFunc}
\end{align}
then we have $\br_{t} = f(\bA_t, \bw_t)$ and $\EE[\br_{t}] = f(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$.

@@

The following lemma provides the important result on the regret at each time $t$ in terms of feature vectors of base arms at the time.

\begin{lemma} %lem:DeltaEstimate
	\label{lem:DeltaEstimate}
	For any time $t$ and $A = (a_1, \ldots, a_{\abs{A}})$, if $f$ satisfies the two assumptions, the properties of monotonicity and Lipschitz continuity, and $f(A_t^*, \bU_t) \leq f(A, \bU_t)$, then we have
	$$
		R(t,A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
	$$
\end{lemma}
\begin{proof}
	By Lemma \ref{lem:estimateU}, $w_t \leq \bU_t$. Then by monotonicity property of $f$,
	$$
	f_t^{\ast} = f(A_t^{\ast}, w_t) \leq f(A_t^{\ast}, \bU_t).
	$$
	By Lipschitz continuity of $f$ and the definition of $\bU_t$ in Eq.\eqref{eq:defU},
	$$
	f(A, \bU_t) \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
	$$
	Then by the condition that $f(A_t^{\ast}, \bU_t) \leq f(A, \bU_t)$, we have 
	$$
	f_t^{\ast} \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
	$$
	Therefore,
	$$
	R(t, A) = f_t^{\ast} - f(A, \theta_{\ast}^{\top}x_t) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
	$$
\end{proof}

@@

\begin{lemma} %lem:DeltaEsimateWithP*
	\label{lem:DeltaEsimateWithP*}
	Suppose the equation (\ref{eq:estimateTheta}) holds for time $t-1$. Then
	$$
	\EE_t[R(t, \bA_t)] \leq \frac{1}{p^*} \EE_t \left[ \bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
	$$
\end{lemma}
\begin{proof}
	\begin{align}
		&\EE[R(t, \bA_t)|\cH_t]  \nonumber \\
		=& \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \label{eq:addOt}\\
		=& \EE \left[ \left. R(t, \bA_t) \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\}  \right| \cH_t \right] \label{eq:removeE}\\
		\leq &\frac{1}{p^{\ast}} \EE \left[ \left. R(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\}  \right| \cH_t \right] \label{eq:relaxpstar}\\
		\leq &\frac{1}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \bOne\{\bO_t = \abs{\bA_t}\}  \right| \cH_t \right] \label{eq:useradiusbound}\\
		\leq &\frac{1}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\bO_t} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \right| \cH_t \right]. \label{eq:relaxindicator}
	\end{align}
	Equality \eqref{eq:addOt} is because when $\bA_t$ is fixed, $p_{t, \bA_t}$ is the probability of $\bO_t = \abs{\bA_t}$, and thus the inner expectation is $1$. Equality \eqref{eq:removeE} is because when the history $\cH_t$ is fixed, $\bA_t$ is fixed by the deterministic algorithm C$^3$-UCB, and thus there is no need to write the conditional expectation. Inequality~\eqref{eq:relaxpstar} is because $p_{t,\bA_t} \geq p^*$ by definition. Inequality~\eqref{eq:useradiusbound} is by Lemma \ref{lem:DeltaEstimate} and the fact $f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t)$, which is true because algorithm C$^3$-UCB selects action $\bA_t$ as the best action with respect to $\bU_t$. Inequality~\eqref{eq:relaxindicator} is by simply arguing on the two cases for the indicator function $\bOne\{\bO_t = \abs{\bA_t}\}$.
\end{proof}

% \begin{lemma} %lem:DeltaEstimate
%   \label{lem:DeltaEstimate}
%   For any time $t$ and $A = (a_1, \ldots, a_{\abs{A}})$, if $f(A_t^*, \bU_t) \leq f(A, \bU_t)$, then we have
%   $$
%     R(t,A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}};
%   $$
%   if $f_{\wedge}(A_t^*, \bU_t) \leq f_{\wedge}(A, \bU_t)$, then we have
%   $$
%     R_{\wedge}(t, A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
%   $$
% \end{lemma}
% \begin{proof}
%   By Lemma \ref{lem:estimateU}, $\theta_{\ast}^{\top}x_t \leq \bU_t$. Then by Lemma \ref{lem:increasing},
%   $$
%     f_t^{\ast} = f(A_t^{\ast}, \theta_{\ast}^{\top}x_t) \leq f(A_t^{\ast}, \bU_t).
%   $$
%   By Lemma \ref{lem:estimateTech} and the definition of $\bU_t$ in Eq.\eqref{eq:defU},
%   $$
%     f(A, \bU_t) \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
%   $$
%   By our condition that $f(A_t^{\ast}, \bU_t) \leq f(A, \bU_t)$, we have 
%   $$
%     f_t^{\ast} \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
%   $$
%   Therefore,
%   $$
%     R(t, A) = f_t^{\ast} - f(A, \theta_{\ast}^{\top}x_t) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
%   $$
%   The result for the conjunctive case can be deduced in a similar way.
% \end{proof}

% Notice that if we substitute $A$ by $\bA_t$ in Lemma \ref{lem:DeltaEstimate}, then the upper bound of $R(t, \bA_t)$ is in terms of all base arms of $\bA_t$. 
% However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains observed base arms. Thus we need the following lemma.

% \begin{lemma} %lem:DeltaEsimateWithP*
%   \label{lem:DeltaEsimateWithP*}
%   Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$.
%   Suppose the equation (\ref{eq:estimateTheta}) holds for time $t-1$. Then
%   $$
%     \EE_t[R(t, \bA_t)] \leq \frac{1}{p^*} \EE_t \left[ \bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
%   $$
%   If we have
%   $$
%     \gamma_K' \le \frac{1}{4} f_{\wedge}^{\ast} = \frac{1}{4} \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast},
%   $$
%   then
%   $$
%     \EE_t [R_{\wedge}(t, \bA_t) ] \leq \frac{8}{f_{\wedge}^{\ast}} \EE_t \left[ \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
%   $$
% \end{lemma}
% \begin{proof}
%   For the disjunctive case,  
%   \begin{align}
%     &\EE[R(t, \bA_t)|\cH_t]  \nonumber \\
%     =& \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \label{eq:addOt}\\
%     =& \EE \left[ \left. R(t, \bA_t) \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right] \label{eq:removeE}\\
%     \leq &\frac{1}{p^{\ast}} \EE \left[ \left. R(t, \bA_t) \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right] \label{eq:relaxpstar}\\
%     \leq &\frac{1}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\abs{\bA_t}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \bOne\{\bO_t\geq\abs{\bA_t}\}  \right| \cH_t \right] \label{eq:useradiusbound}\\
%     \leq &\frac{1}{p^{\ast}} \EE \left[ \left. \sum_{k=1}^{\bO_t} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}} \right| \cH_t \right]. \label{eq:relaxindicator}
%   \end{align}
%   Equality \eqref{eq:addOt} is because when $\bA_t$ is fixed, $p_{t, \bA_t}$ is the probability of $\bO_t\geq\abs{\bA_t}$, and thus the inner expectation is $1$. 
%   Equality \eqref{eq:removeE} is because when the history $\cH_t$ is fixed, $\bA_t$ is fixed by the deterministic algorithm C$^3$-UCB, and thus there is no need to write the conditional expectation. 
%   Inequality~\eqref{eq:relaxpstar} is because $p_{t,\bA_t} \geq p^*$ by definition. 
%   Inequality~\eqref{eq:useradiusbound} is by Lemma \ref{lem:DeltaEstimate} and the fact $f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t)$, which is true because algorithm C$^3$-UCB selects action $\bA_t$ as the best action with respect to $\bU_t$. 
%   Inequality~\eqref{eq:relaxindicator} is by simply arguing on the two cases for the indicator function $\bOne\{\bO_t\geq\abs{\bA_t}\}$.

%   For the conjunctive case, by Lemma~\ref{lem:prefixexists} there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, t, \bB_t} \geq \frac{1}{2}f_{\wedge, t}^* - \gamma'_{|\bB_t|}$ and $R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t)$. 
%   By the assumption that $\gamma'_{|\bB_t|}\le \gamma'_K \le \frac{1}{4} f^*_{\wedge} \le \frac{1}{4} f^*_{\wedge,t}  $, we have $p_{\wedge, t, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$. 
%   Then, similar to the derivation from Eq.\eqref{eq:addOt} to Eq.\eqref{eq:relaxpstar}, we have
%   \begin{align}
%     &\EE_t[R_{\wedge}(t, \bA_t)] \leq 2 \EE[R_{\wedge}(t, \bB_t) \left. \right| \cH_t] \nonumber \\
%     =& 2 \EE \left[ \left. R_{\wedge}(t, \bB_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\} \right| \bB_t \right]  \right| \cH_t \right] \nonumber \\
%     =& 2\EE \left[ \left. R_{\wedge}(t, \bB_t) \frac{1}{p_{\wedge, t, \bB_t}} \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right] \nonumber \\
%     \leq &\frac{8}{f_{\wedge, t}^{\ast}} \EE \left[ \left. R_{\wedge}(t, \bB_t) \bOne\{\bO_t\geq\abs{\bB_t}\}  \right| \cH_t \right]. \label{eq:btOneotbt}
%   \end{align}
%   Next, we have
%   \begin{equation} \label{eq:andstarbt}
%     f_{\wedge}(A_t^*, \theta_*^{\top}x_t) \leq f_{\wedge}(A_t^*,\bU_t) \leq f_{\wedge}(\bA_t,\bU_t) \leq f_{\wedge}(\bB_t,\bU_t),
%   \end{equation}
%   where the first inequality is by Lemmas \ref{lem:estimateU} and \ref{lem:increasing}, the second inequality is by the C$^3$-UCB algorithm, in which the best action $\bA_t$ is selected with respect to $\bU_t$, and the last inequality is by Lemma~\ref{lem:prefixRelation}~(2).
